InformatiCup 2024 Ctrl-Alt-Defeat

### 2023-12-04 paper.tex
Incoorporate rephrasing

The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2. It was obtained by fine-tune a RoBERTa base model with the ouputs of the GPT-2 model containing 1,5 Billion parameters. RoBERTa Base OpenAI Detector can be used to classify text, on whether it is likely to be created by the GPT-2 model. It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.

\section{Method}

>>>>

\section{Method}
To test and evaluate the effect of different data augmentation techniques on the detection capabilities of fake image or text detectors, we created a pipeline of three components: The first component is a generator, which is a model capable of generating fake images or texts. The second component is a processor which augments the data through a specified method, after inputting a generated image or text. The last component is a detector, which suggests an input being either real or fake. This way we can compare it to the ground truth, to evaluate the capabilities of the detector. By comparing the results with augmented artefacts and with the generated ones without augmentation, we can evaluate the effectiveness of different AI detector-tricking techniques.
